Modelling Structured Societies: a Multi-relational Approach to Context Permeability

### 2014-09-28 doc/main.tex
review1: most of the issues were addressed, the only thing left is to put the doi and review the bibliography

	%******************************************
	%		Related Work
	%******************************************
	\section{Related Work}
	\label{sec:relatedwork}
	In this section, we present work related to, \textit{opinion dynamics}, \textit{social space} modelling and \textit{complex network models}.	
	%******************************************
	%	Opinion Dynamics
	%******************************************
	\subsection{Opinion Dynamics and Consensus Formation}
	Formal opinion dynamics models provide an understanding, if not an analysis, of opinion formation processes.  An early formulation of these models was designed to comprehend complex phenomena found empirically in groups \cite{French1956}. In particular, the work on consensus building in the context of decision-making was first studied by DeGroot \cite{Degroot74} and Lehrer \cite{Lehrer1975}. Empirical studies of opinion formation in large populations have methodological limitations, as such, computational sociology arises with a set of tools to cope with those limitations. We use simulation, in particular \textit{multi-agent simulation (MAS)}, as a methodological framework to study such phenomena in a larger scale. Most opinion dynamics simulation models are based either on binary opinions \cite{Galam1997,Antunes2009} or continuous values \cite{Deffuant2000,Deffuant2002}. In these models, agents update their opinions either under social influence or according to their own experience. For a detailed analysis over some opinion dynamics model analytical and simulation results, refer to \cite{Hegselmann2002}.

	§§§ ESTA ULTIMA FRASE ESTÁ ESTRANHA!!! falta uma vírgula antes de model? mesmo assim não se perceberia bem... Podes rever, pf?

@@

	%******************************************
	%	Social Structure in Simulation Models
	%******************************************
	\subsection{Social Structure in Simulation Models}
	One of the most widely used approaches to represent social spaces in abstract simulation models is using a  bi-dimensional grid. This approach has its origins in the first \textit{‚Äúcheckerboard‚Äù} 
	§§§ VER AQUI
	model introduced in computational social sciences by Thomas Schelling \cite{Schelling1971} and Sakoda \cite{Sakoda1971}. Another famous example that uses bi-dimensional grids as social structure is the social simulation model of dissemination of culture from Axelrod \cite{Axelrod1997}.

@@

	%******************************************
	%	Complex Network Models
	%******************************************	
	Finally, another type of social space models are the \textit{random graph/network models}. Networks with different properties can be built using network models. Each complex network or class of complex networks, presents specific topological features. These properties are typically found in---and the models inspired by---real-world network structures. One of the first complex network models is the random graph from §§§ VER Erd≈ës and Renyi \cite{Erdos1959}. Other examples include the model of preferential attachment \cite{Barabasi1999} and the small-world network models \cite{Watts1998}. One common problem of these models is the fact that once generated, the network structure is static so these models are not really suitable for the description of highly dynamic groups or communities. An example of a model that takes these dynamics into account is the model of team formation~\cite{Gaston2005}. A more in-depth review of network models and their properties is given in~\cite{Nunes2012}.

@@

	§§§ TALVEZ ACRESCENTAR ISTO??? The reason we are not really interested in which exact option gets selected is the same reason why we chose such a content-neutral game for the individual interactions. From the very beginning, our research questions were focused on the collective properties, the structure of the networks involved, and the dynamical outcomes of the simulations, thus leaving out issues related with individual motivations and desired results, either for any individual agent or the society. Granted, most applications of this research will often include such goals, for inquisition into complex social issues, including possibly policy design, in which the individual rationalities must be considered, and will have a very strong influence on the collective outcomes. We opted not to taint the simulation with such matters, leaving that very interesting approach for future work.

@@

	\subsection{Context Switching}
	\label{sec:models_cs}
	In the context switching model \cite{Antunes2009}, agents are embedded in multiple relations represented as static social networks and they switch \textit{contexts} with a given probability $\zeta_{C_i}$ associated with context $C_i$. The switching probability value is §§§VERIFICA SE É ISTO§§§ kept constant for any given network.§§§TIRAR  the same in the same network.§§§ Each agent switches from its current neighbourhood to a further §§§(vê pf se further está bem, fiquei na dúvida o que querias dizer) neighbourhood in another network (in which this agent was inactive). The agents are only active in one context at a time, and can only perform encounters with neighbours in the same context. We can think of context switching as a temporary deployment in another place, such as what happens with temporary immigration. The network topology is static; when an agent switches from one network to another, they become inactive in one network and active in their destination. 
	%***************************************************
	%	Context Switching Model Description
	%***************************************************
	\begin{algorithm}[H]
		\caption{Context Switching}
		\label{model:context_switching}
		\algsetup{indent=2em}
		\begin{algorithmic}
			\vspace{0.5em}
			\STATE $M$ \COMMENT{Simulation Model / Environmnet}
			\STATE $A$ \COMMENT{Current Agent in Execution}
			\\ \hrulefill

@@

§§§acho que se devia explicar primeiro o que **são** scale-free networks, o que as define, e só depois dizer que se podem construir com o preferential attachment, aliás, não é a única maneira de as construir, nem sei se é a melhor, apenas á a mais usual e usada...§§§

Scale-free networks \cite{Barabasi1999} are created with a model of preferential attachment proposed by Barab\'{a}si and colleagues \cite{Barabasi1999}. This model builds upon the perception of a common property of many large networks, a scale-free-power-law distribution of node connectivity. This feature was found to be a consequence of two generic mechanisms: networks expand continuously by the addition of new vertices, and new vertices attach preferentially to sites that are already well connected, being this mechanism more commonly known as ``preferential attachment''. In these networks, the probability $P(k)$ of two nodes being connected to each other decays as a power law, following $P(k) \sim k^{- \gamma}$.

The network instances were generated using the \textit{b-have network library} §§§cita tb o paper do MABS 2013? \cite{Nunes:Software:11069}. This is a Java library that allows for the manipulation of Network/Graph data structures. It also includes the more commonly used random network models from the literature.

\subsection{Measuring Network Properties}
We measure two structural properties of our networks: the \textit{average path length} and the \textit{clustering coefficient}. The \textit{average path length} measures the typical separation between two vertices in the graph. The \textit{clustering coefficient} measures the average cliquishness of the graph neighbourhood. This measure quantifies how close the neighbours of a node are to forming a clique. Duncan J. Watts and Steven Strogatz \cite{Watts1998} introduced the measure to characterise a class of complex networks called small-world networks. The networks produced by the \textit{b-have network library} \cite{Nunes:Software:11069} were exported to files and analysed using the \textit{igraph R package} \cite{igraph2006}.

§§§ TALVEZ UM POUCO MAIS SOBRE O SIGNIFICADO DESSAS MEDIDAS, E DAÍ O SEU VALOR PARA OS ESTUDOS DE FENOMENOS SOCIAIS COMPLEXOS

@@

% Overview
In this section, we bababa
§§§

@@

§§§ regra== "xxx that" ou "xxx, which"

@@

\subsubsection{Properties of Overlapping K-Regular Networks}
\label{sec:overlapping_kreg}
We will now investigate what kind of properties we can get from merging k-regular networks. First, we analysed the distribution for the average path length and the clustering coefficient values over 100 network instances with 100 nodes each. Since this variation §§§qual variation??? do average path length???§§§ is negligible, we use the average as a descriptor for different configurations of k values and number of overlapping networks. (The reader should refer to figures \ref{append_fig:network_properties_apl_kreg} and \ref{append_fig:network_properties_cc_kreg} in the appendix for the box plot preliminary analysis.)

@@

\noindent Figure \ref{fig:network_properties_line_cc_sf_kreg} shows the results for the \textit{clustering coefficient}. These are similar to the results we get for \textit{k-regular} networks (see figure \ref{network_properties_cc_line_kreg}). The difference is that we are not adding more networks but rather increasing the parameter $d$ of the scale-free. Curiously, in this case, the effects are qualitatively similar with the ones of merged \textit{k-regular} network with low value of $k$. With high values of $k$ (figure \ref{fig:network_properties_cc_line_sf_kreg_1020304050}) we can see that higher values of $d$ are not enough to make the network more clustered. This happens because scale-free networks are more sparse and have a very low number of triangles between nodes.

@@

The following tables show the results of our simulations. Table ~\ref{tab:regular_convergence} shows the percentage of total consensus achieved with 2000 cycles for 3000 runs. We can see that for k-regular networks with a small $k$, consensus is rarely achieved with a single network. However, as soon as we add more networks, consensus is achieved in a significantly greater number of occasions. These results are especially interesting for the \textit{scale-free }networks (table \ref{tab:scale-free_convergence}): as soon as we add more planes, for a \textit{scale-free} with $d\ge2$, we can achieve consensus in a lot of occasions. This is to show that achieving consensus is not just a matter of connectivity. With \textit{scale-free} networks, we can achieve consensus more often with less clustered networks. This convergence is achieved not because of the clustering coefficient but rather due to lower \textit{average path length}. This is difficult to visualise using only the tables and the previous plots so, to confirm this hypothesis, we measured the \textit{Spearman's correlation} between the ratio of convergences to consensus, the average of \textit{average path length} , and the average of \textit{clustering coefficient} for the corresponding network configurations (see table \ref{tab:convergence_correlation}).

§§§ talvez explicar o que significa a Spearman's correlation ???

@@

§§§ ACHO QUE ESTAMOS A GASTAR UM BOCADO DE TEMPO/ESPAÇO A MAIS COM ESTE "OUTLIER RUN" OU ISSO CONDUZ A UMA CONCLUSÃO FORTE E IMPORTANTE, OU ESTAMOS SUJEITOS A ALGUMA CRÍTICA AQUI

@@

\noindent One of the differences §§§entre quê e quê???, fica dificil sem as imagens no meio §§§ lies in the configuration with $d=1$ and $k=1$. The convergence ratio is higher than with $2$ $1-regular$ networks (see table \ref{tab:regular_convergence}) --but not better than two \textit{scale-free} networks. This happens because with $k=1$ the network is basically a ring and has the maximum possible average path length for a connected graph. Adding two rings improves §§§improves WHAT???§§§ this but the underlying structure is still very susceptible to self-reinforcing structures (a connected sub-graph is basically a line). Adding a \textit{scale-free} changes this drastically as we are mixing tree-like network components with this first circle.

@@

§§§ ATENçÂO QUE ``deve fechar com '' (duas plicas), não com " (aspas)

@@

To check the influence of topology and connectivity in the new switching dynamics we took the most susceptible (§§§TO WHAT???) network type (the \textit{scale-free} networks) and performed the following experiment. We setup two \textit{scale-free} networks; one with $d=1$ and the other with $d=5$. We then performed the 
same span of switching probability similarly to the previous experiments. The results can be seen in figure \ref{fig:ctx_cs_sf_d5_d1}.

@@

The surprise was that for values of $k \ge 20$, the results where practically the same for both models independently of the switching probability --even when we increased the number of networks, the number of encounters remained around $2000$ on average for all the models. Above a certain level of neighbourhood size (and overlapping, which causes the average path length to drop), the switching probability becomes less influential. It is still important that we get comparable results because we are introducing a temporal component that was never explored before in these types of opinion dynamics models: the fact that the agents can become active in different networks at different points in time.
§§§ mudei . para : na ultima frase, por favor valida

@@

For \textit{scale-free} networks, figure \ref{ctx_switching_comp_sf} shows us similar results. It seems that switching with a higher probability displays results similar with those of context permeability. In this case, adding more networks makes so that lowering switching probabilities displays slightly worse results. This influence is due to the fact that the neighbourhoods are considerably smaller in \textit{scale-free} networks --even with values of $d=5$-- so the impact of low switching was bound to be noticed.

One final remark is that with context switching, we always achieve consensus §§§ não percebo este being, será de cortar?§§§ being for \textit{k-regular} or \textit{scale-free} networks. In addition, increasing the number of networks seems to always reduce the number of encounters to achieve consensus in both models. This happens due to what we have called \textit{permeability}. Having multiple points of dissemination that permeate between different social networks enhances the overall convergence to consensus. §§§ acrescentei <<With permeability there are more previously >>§§§ With permeability there are more previously isolated nodes being reached in sparsely connected networks such as scale-free networks.

§§§ não falaste de context switching induzido por razões, suponho que é intencional para deixar algo para um futuro paper, e também porque este já vai longo...
§§§

@@

Future work includes the analysis of different complex network models, §§§while??? será although? §§§ while \textit{k-regular} and \textit{scale-free} networks are two of the most pervasive network examples in these types of simulations. There has been a growing number of models with different properties inspired by real-world phenomena that can be considered. We can also analyse the networks according to different properties such as the present of nodes with high centrality in the network (hubs). Moreover, we  plan to apply what we learned with our consensus games to cooperation problems. Constructing agents that can learn both behaviour and coordination procedures is a difficult task especially when working with large distributed artificial societies. Consensus games such as this one can be used to reduce the search space in problems where agents need to cooperate or coordinate.

@@

We have seen that context permeability by context overlapping or switching can provide a fairly straightforward modelling methodology that can be used to compose simulation scenarios for more complex social spaces. What remains to be done is to identify more precise contextual structures in real-world networks. While capturing the structure of real social network can be a daunting task, we do have pervasive records of networking activity between social actors: online social networks. Analysing these can lead us to insights about complex structural properties that emerge from user activity, and context that can be identified within those networks. A difficult --but not impossible-- prospect for further research would be to track similar contexts between different real online social networks. 	§§§ isto vem na linha do que eu acrescentei acima sobre manter o jogo neutro, para nos concentrarmos na estrutura do problema, talvez seja de ir lá buscar umas frases, e acerescentá-las aqui, que justificam que não nos debruçámos sobre dados reais, porque nos interessava mais a estrutura matemática...

We are just scratching the surface of multi-relational models in social simulation with the next step being the connection of our model to the reality. §§§ esta frase enfraquece um pouco as conclusões e o artigo, não achas???

>>>>

	%******************************************
	%		Related Work
	%******************************************
	\section{Related Work}
	\label{sec:relatedwork}
	In this section, we present work related to, \textit{opinion dynamics}, \textit{social space} modelling and \textit{complex network models}.	
	%******************************************
	%	Opinion Dynamics
	%******************************************
	\subsection{Opinion Dynamics and Consensus Formation}
	Formal opinion dynamics models provide an understanding, if not an analysis, of opinion formation processes.  An early formulation of these models was designed to comprehend complex phenomena found empirically in groups \cite{French1956}. In particular, the work on consensus building in the context of decision-making was first studied by DeGroot \cite{Degroot74} and Lehrer \cite{Lehrer1975}. Empirical studies of opinion formation in large populations have methodological limitations, as such, computational sociology arises with a set of tools to cope with those limitations. We use simulation, in particular \textit{multi-agent simulation (MAS)}, as a methodological framework to study such phenomena in a larger scale. Most opinion dynamics simulation models are based either on binary opinions \cite{Galam1997,Antunes2009} or continuous values \cite{Deffuant2000,Deffuant2002}. In these models, agents update their opinions either under social influence or according to their own experience. For a detailed analysis over some opinion dynamics models, refer to \cite{Hegselmann2002}.

@@

	%******************************************
	%	Social Structure in Simulation Models
	%******************************************
	\subsection{Social Structure in Simulation Models}
	One of the most widely used approaches to represent social spaces in abstract simulation models is using a  bi-dimensional grid. This approach has its origins in the first \textit{``checkerboard''} model introduced in computational social sciences by Thomas Schelling \cite{Schelling1971} and Sakoda \cite{Sakoda1971}. Another famous example that uses bi-dimensional grids as social structure is the social simulation model of dissemination of culture from Axelrod \cite{Axelrod1997}.

@@

	%******************************************
	%	Complex Network Models
	%******************************************	
	Finally, another type of social space models are the \textit{random graph/network models}. Networks with different properties can be built using network models. Each complex network or class of complex networks, presents specific topological features. These properties are typically found in---and the models inspired by---real-world network structures. One of the first complex network models is the random graph from Erd\H{o}s and Rényi \cite{Erdos1959}. Other examples include the model of preferential attachment \cite{Barabasi1999} and the small-world network models \cite{Watts1998}. One common problem of these models is the fact that once generated, the network structure is static so these models are not really suitable for the description of highly dynamic groups or communities. An example of a model that takes these dynamics into account is the model of team formation~\cite{Gaston2005}. A more in-depth review of network models and their properties is given in~\cite{Nunes2012}.

@@

	The reason we are not really interested in which exact option gets selected is the same reason why we chose such a content-neutral game for the individual interactions. From the very beginning, our research questions were focused on the collective properties, the structure of the networks involved, and the dynamical outcomes of the simulations: thus leaving out issues related with individual motivations and desired results, either for any individual agent or the society. Granted, most applications of this research will often include such goals, for inquisition into complex social issues, including possibly policy design, in which the individual rationalities must be considered, and will have a very strong influence on the collective outcomes. We opted not to taint the simulation with such matters, leaving that very interesting approach for future work.

@@

	\subsection{Context Switching}
	\label{sec:models_cs}
	In the context switching model \cite{Antunes2009}, agents are embedded in multiple relations represented as static social networks and they switch \textit{contexts} with a given probability $\zeta_{C_i}$ associated with context $C_i$. The switching probability value is the same for every agent in a given network.  Each agent switches from its current neighbourhood to another network (in which this agent was inactive). The agents are only active in one context at a time, and can only perform encounters with neighbours in the same context. We can think of context switching as a temporary deployment in another place, such as what happens with temporary immigration. The network topology is static; when an agent switches from one network to another, they become inactive in one network and active in their destination. 
	%***************************************************
	%	Context Switching Model Description
	%***************************************************
	\begin{algorithm}[H]
		\caption{Context Switching}
		\label{model:context_switching}
		\algsetup{indent=2em}
		\begin{algorithmic}
			\vspace{0.5em}
			\STATE $M$ \COMMENT{Simulation Model / Environmnet}
			\STATE $A$ \COMMENT{Current Agent in Execution}
			\\ \hrulefill

@@

Scale-free networks are networks in which the degree distribution follows a power law, at least asymptotically. That is, the fraction $P(k)$ of nodes in the network having $k$ connections to other nodes goes for large values of $k$ as: $ P(k)  \sim  k^{-\gamma}$ where $\gamma$ is a parameter whose value is typically in the range $2 < \gamma < 3$.

We use the method proposed in \cite{Barabasi1999} by Barab\'{a}si and Albert to construct the scale-free network instances using a preferential attachment. This model builds upon the perception of a common property of many large networks, a scale-free-power-law distribution of node connectivity. This feature was found to be a consequence of two generic mechanisms: networks expand continuously by the addition of new vertices, and new vertices attach preferentially to sites that are already well connected, being this mechanism more commonly known as ``preferential attachment''. In these networks, the probability $P(k)$ of two nodes being connected to each other decays as a power law, following $P(k) \sim k^{- \gamma}$.

The network instances were generated using the \textit{b-have network library} \cite{Nunes:Software:11069}. This is a Java library that allows for the manipulation of Network/Graph data structures. It also includes the more commonly used random network models from the literature.

\subsection{Measuring Network Properties}
We measure two structural properties of our networks: the \textit{average path length} and the \textit{clustering coefficient}. The \textit{average path length} measures the typical separation between two vertices in the graph. The \textit{clustering coefficient} measures the average cliquishness of the graph neighbourhood. This measure quantifies how close the neighbours of a node are to forming a clique. Duncan J. Watts and Steven Strogatz \cite{Watts1998} introduced the measure to characterise a class of complex networks called small-world networks.

These properties are quite important to study social phenomena as they characterize structures that 
can be found in the real scenarios. The small-world networks generated by the models of Watts and Strogatz for instance \cite{Watts1998}, tries to model real-world social networks with short average path length, generate local clustering, and triadic closures between the nodes. One shortcoming of this model, is the fact that these networks do not possess node hubs found in many real-world social networks.

Since we construct scenarios where we overlap highly clustered k-regular networks and scale-free networks with node hubs, we are interested in what kind of properties emerge from merging these structures and how they are comparable to the existing models.

The networks produced by the \textit{b-have network library} \cite{Nunes:Software:11069} were exported to files and analysed using the \textit{igraph R package} \cite{igraph2006}.

@@

% Overview
In this section, we analyse and discuss the results for different experiments with both the
context permeability and context switching models. We start by analysing the structural properties
that arise from combining different networks while maintaining the same set of network nodes. We then perform multiple experiments where we observe the impact of different model configurations in the convergence to consensus. We correlate the outcomes of our context permeability model simulations with the structural properties of the multi-network structures. We also explore how the new dynamics introduced by the context switching model, affect the consensus building process.

@@

@@

\subsubsection{Properties of Overlapping K-Regular Networks}
\label{sec:overlapping_kreg}
We will now investigate what kind of properties we can get from merging k-regular networks. First, we analysed the distribution for the average path length and the clustering coefficient values over 100 network instances with 100 nodes each. From a box plot preliminary analysis (see figures \ref{append_fig:network_properties_cc_kreg} and \ref{append_fig:network_properties_apl_kreg}), we can see that the average path length does not vary much for the 100 instances, as such, we use the average as a descriptor for different configurations of k values and number of overlapping networks.

@@

\noindent Figure \ref{fig:network_properties_line_cc_sf_kreg} shows the results for the \textit{clustering coefficient}. These are similar to the results we get for \textit{k-regular} networks (see figure \ref{fig:network_properties_cc_line_kreg}). The difference is that we are not adding more networks but rather increasing the parameter $d$ of the scale-free. Curiously, in this case, the effects are qualitatively similar with the ones of merged \textit{k-regular} network with low value of $k$. With high values of $k$ (figure \ref{fig:network_properties_cc_line_sf_kreg_1020304050}) we can see that higher values of $d$ are not enough to make the network more clustered. This happens because scale-free networks are more sparse and have a very low number of triangles between nodes.

@@

The following tables show the results of our simulations. Table ~\ref{tab:regular_convergence} shows the percentage of total consensus achieved with 2000 cycles for 3000 runs. We can see that for k-regular networks with a small $k$, consensus is rarely achieved with a single network. However, as soon as we add more networks, consensus is achieved in a significantly greater number of occasions. These results are especially interesting for the \textit{scale-free }networks (table \ref{tab:scale-free_convergence}): as soon as we add more planes, for a \textit{scale-free} with $d\ge2$, we can achieve consensus in a lot of occasions. This is to show that achieving consensus is not just a matter of connectivity. With \textit{scale-free} networks, we can achieve consensus more often with less clustered networks. This convergence is achieved not because of the clustering coefficient but rather due to lower \textit{average path length}. This is difficult to visualise using only the tables and the previous plots so, to confirm this hypothesis, we measured the \textit{Spearman's correlation}\footnote{The Spearman's rank correlation coefficient is a nonparametric measure of statistical dependence between two variables. It assesses how well the relationship between two variables can be described using a monotonic function.} between the ratio of convergences to consensus, the average of \textit{average path length} , and the average of \textit{clustering coefficient} for the corresponding network configurations (see table \ref{tab:convergence_correlation}).

@@

@@

\noindent One of the outcome differences between this configuration and the previous ones can be observed in the simulations with $d=1$ and $k=1$. The convergence ratio is higher than with $2$ $1-regular$ networks (see table \ref{tab:regular_convergence}) --but not better than two \textit{scale-free} networks. This happens because with $k=1$ the network is basically a ring and has the maximum possible average path length for a connected graph. Adding two rings improves  the convergence ratio but the underlying structure is still very susceptible to self-reinforcing structures (a connected sub-graph is basically a line). Adding a \textit{scale-free} changes this drastically as we are mixing tree-like network components with this first circle.

@@

@@

To check the influence of connectivity in the new switching dynamics we setup two \textit{scale-free} networks; one with $d=1$ and the other with $d=5$. We then performed the 
same span of switching probability similarly to the previous experiments. The results can be seen in figure \ref{fig:ctx_cs_sf_d5_d1}.

@@

The surprise was that for values of $k \ge 20$, the results where practically the same for both models independently of the switching probability --even when we increased the number of networks, the number of encounters remained around $2000$ on average for all the models. Above a certain level of neighbourhood size (and overlapping, which causes the average path length to drop), the switching probability becomes less influential. It is still important that we get comparable results because we are introducing a temporal component that was never explored before in these types of opinion dynamics models: the fact that the agents can become active in different networks at different points in time.

@@

For \textit{scale-free} networks, figure \ref{fig:ctx_switching_comp_sf} shows us similar results. It seems that switching with a higher probability displays results similar with those of context permeability. In this case, adding more networks makes so that lowering switching probabilities displays slightly worse results. This influence is due to the fact that the neighbourhoods are considerably smaller in \textit{scale-free} networks --even with values of $d=5$-- so the impact of low switching was bound to be noticed.

An increasing number of networks seems to always reduce the number of encounters to achieve consensus in both models. This happens due to what we have called \textit{permeability}. Having multiple points of dissemination that permeate between different social networks enhances the overall convergence to consensus. With permeability there are more previously isolated nodes being reached in sparsely connected networks such as scale-free networks.

@@

The second innovation presented in this paper was the fact that our model describes an abstract way to represent the time spent on each network using the switching probability. This temporal component introduces a new dynamic to the study of opinion dynamics. Considering that in agent neighbourhoods, agents might not be available at all times and spend distinct amounts of time in different neighbourhoods, is an important factor to be included in some simulations from a modelling perspective.

Future work includes the analysis of different complex network models. While \textit{k-regular} and \textit{scale-free} networks are two of the most pervasive network examples in these types of simulations, there has been a growing number of models with different properties inspired by real-world phenomena that can be considered. We can also analyse the networks according to different properties such as the present of nodes with high centrality in the network (hubs). Moreover, we  plan to apply what we learned with our consensus games to cooperation problems. Constructing agents that can learn both behaviour and coordination procedures is a difficult task especially when working with large distributed artificial societies. Consensus games such as this one can be used to reduce the search space in problems where agents need to cooperate or coordinate.

@@

We have seen that context permeability by context overlapping or switching can provide a fairly straightforward modelling methodology that can be used to compose simulation scenarios for more complex social spaces. What remains to be done is to identify more precise contextual structures in real-world networks. While capturing the structure of real social network can be a daunting task, we do have pervasive records of networking activity between social actors: online social networks. Analysing these can lead us to insights about complex structural properties that emerge from user activity, and context that can be identified within those networks. A difficult --but not impossible-- prospect for further research would be to track similar contexts between different real online social networks.
